\cvsection{Experience}
\begin{cventries}

\cventry
{Graduate Student Instructor}
{University of Maryland, Baltimore County (UMBC)}
{Baltimore, MD}
{August 2016}
{
    \begin{cvitems}
        \item{Deliver two lectures a week for the introductory computer science course (CMSC 201)}
        \item{Contribute heavily to the curriculum design, assignments, and exams}
    \end{cvitems}
}

\cventry
{Technical Intelligence Intern}
{Hewlett Packard Enterprise}
{Hanover, MD}
{May 2016 - PRESENT}
{
    \begin{cvitems}
        \item{Cognitive Computing Toolkit.}
    \end{cvitems}
}

\cventry
{Graduate Teaching Assistant}
{University of Maryland, Baltimore County (UMBC)}
{Baltimore, MD}
{August 2015 - July 2016}
{
    \begin{cvitems}
        \item {Acted at Head Teaching Assistant for the introductory computer science course (CMSC 201)}
        \item {Administered the assignment submission system}
        \item {Developed Python scripts to grade several hundred students efficiently, and quickly capture and report those grades}
        \item {Contribute to assignment development}
        \item {Oversaw 40 undergraduate and graduate teaching assistants}
    \end{cvitems}
}
    

\cventry
{Technical Intern}
{The Johns Hopkins Applied Physics Laboratory}
{Laurel, MD}
{May 2015 - August 2015}
{
    \begin{cvitems}
        \item{Researched the use of and presented findings on Apache Zookeeper.}
        \item{Designed a solution for the coordination of nodes in a distributed graph processing system using that technology.}
        \item{Implemented a web scraper for publicly available medical records to generate feature vectors for machine learning applications.}
    \end{cvitems}
}

\cventry
{Technical Intern}
{The Johns Hopkins Applied Physics Laboratory}
{Laurel, MD}
{May 2014 - August 2014}
{
    \begin{cvitems}
        \item{Researched the design of the open source cloud computing project, Openstack.}
        \item{Contributed to the development of a lab-wide Infrastructure as a Service for testing software in a controlled environment.}
        \item{Wrote software tools or the automation of cloud related tasks.}
    \end{cvitems}
}

\cventry
{Program Assistant}
{The Johns Hopkins University Center for Talented Youth}
{Sandy Spring, MD}
{June 2013 - August 2013}
{
    \begin{cvitems}
        \item{Ran around with children all day.}
    \end{cvitems}
}


\end{cventries}
